Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-03-09 paper/main.tex
Got Alignment stage runtime plot into the paper
Added alignment stage rank plot

In Figure \ref{fig:alignment_stage_runtime} we report the time it takes
to align a single test image against each of the users in the gallery.
We vary the size of the gallery to show how implementation scales in the
number of gallery users.
%\begin{figure}
%\centering
%\include{figures/alignment_stage_runtime.tex}
%%\includegraphics[width=3.5in]{figures/alignment_stage_runtime.pdf}
%\caption{Alignment Stage Runtime vs. Size of Training Database}
%\label{fig:alignment_stage_runtime}
%\end{figure}

>>>>

In Figure \ref{fig:alignment_stage_runtime} we report the time it takes
to align a single test image against each of the users in the gallery.
We vary the size of the gallery to show how implementation scales in the
number of gallery users.
\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/alignment_runtime_graph}
\caption{Alignment Stage Runtime vs. Size of Training Database}
\label{fig:alignment_stage_runtime}
\end{figure}

Previous publications used a hard threshold on the number of subjects kept for the recognition
stage as a compromise between recognition speed and potential recognition rate.
In order to better motivate 
a choice for a threshold of the number of users kept for the recognition stage,
we varied the number of users kept for the recognition stage and estimated the probability
of the test user being among the set of training users kept for the recognition stage.
As can be seen in Figure \ref{fig:user_alignment_rank_plot}, there are rapidly diminishing
returns as the number of kept users is increased beyond ten.  
\begin{figure}
\centering
\includegraphics[width=3.4in]{figures/user_alignment_rank_plot}
\caption{Probability of the test user being kept for the recognition stage vs. Number of traning
users kept for the recognition stage}
\label{fig:user_alignment_rank_plot}
\end{figure}
